---
title: "Market Share Analysis"
author: "Pallak Goyal"
date: "2024-01-03"
output: word_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Methodology

- Only Category 1 and Category 3 beneficiaries were considered.
- The consolidated statements contain the total sales of all goods sold by the company. These goods differ even at the two digit level. Therefore sales data was taken from the Standalone annual financial statements.
- For each year the respective two digit nic classification was considered for determination of market share.
- The market share was calculated by dividing the total sales of goods of that company by the total sales of goods of all companies that were at the same two-digit classification.
- For the years when sales were not available the data point was dropped and calculations were done.
- The beneficiaries were classified as micro, small, medium and large following the revised turnover definition by the Ministry of Micro, Small and Medium Enterprises. Under this method, turnover less than or equal to 5 crore is classified as micro, above 5 crore but less than or equal to 50 crore is classified as small and above 50 crore but less than or equal to 250 crore is classified as medium.
- 2023 data is not considered as it is not comparable since the base is smaller due to unavailability of data at present. Also, within beneficiaries, the data is available for less than 50% for this year.
- In order to establish causality of market share with a time series data one would need the data on prices charged by the firm and its competitors^[For example see @mixon_determinants_1997,@weiss_determinants_1968]. This data is not available so the results are only illustrative and do not establish causality. 
- For small and medium size firms a control group is formed to establish causality of changes in market share.

## Heat Maps of Market Shares

The heat maps are drawn using a scaling at the enterprise level.
```{r code, include=FALSE}
# The purpose of this file is to get the market share for the beneficiaries of the firms in categories 1 and 3 of the PLIFPI. The basis is going to be total sales of goods field in the standalone annual financial statements. 

# Loading the identity details of the beneficiaries.
identity <- read.table("./identity.txt", header = T,sep = "|", na.strings="", comment.char = "", quote = "\"", fill = F,nrows = 74)

# loading the history of classification of the beneficiaries.
class <- read.table("./class.txt", header = T,sep = "|", na.strings="", comment.char = "", quote = "\"", fill = F,nrows = 2713)
# asking r to read the dates as such
class[,3] <- format(as.Date(as.character(class[,3]), "%Y%m%d"), "%Y")
# adding a column of nic codes at 2 digit level
nic_code_two_digit <- as.numeric(substr(as.character(class[,7]), 1, 2))
class <- cbind(class,nic_code_two_digit)
# taking only annual reports based classification
class <- class[class$mr_info_full_name=="Annual Report",]
# considering only the years 2017-2023
class <- class[class$coprd_date=="2017"|class$coprd_date=="2018"|class$coprd_date=="2019"|class$coprd_date=="2020"|class$coprd_date=="2021"|class$coprd_date=="2022"|class$coprd_date=="2023",]
# load the sales data.
sales <- read.table("./sales.txt", header = T,sep = "|", na.strings="", comment.char = "", quote = "\"", fill = F,nrows = 466)
# getting the sales data in a desirable format
sales[,6] <- as.numeric(sales[,6])
sales[,3]<- format(as.Date(as.character(sales[,3]), "%Y%m%d"), "%Y")
# creating same column names to help merge data
colnames(class)[1] <- "prowess_code"
colnames(sales)[1] <- "prowess_code"
colnames(class)[3] <- "year"
colnames(sales)[3] <- "year"
colnames(sales)[2] <- "company_name"
# merging data 
sales_by_class <- merge(x = sales, y = class, by = c("prowess_code","year","company_name"), all.x = TRUE)
# getting rid of the less likely to be used columns
sales_by_class <- sales_by_class[,c(1,2,3,6,12)]
# loading sales data for all prowess companies in the relevant years
sales_all <- read.table("./sales_all.txt", header = T,sep = "|", na.strings="", comment.char = "", quote = "\"", fill = F,nrows = 218552)
# getting the sales_all data in desirable format
sales_all[,3] <- format(as.Date(as.character(sales_all[,3]), "%Y%m%d"), "%Y")
sales_all[,6] <- as.numeric(sales_all[,6])
# getting classification data for all companies
class_all <- read.table("class_all.txt", header = T,sep = "|", na.strings="", comment.char = "", quote = "\"", fill = F,nrows = 332327)
# formatting the date in class_all
class_all[,3] <- format(as.Date(as.character(class_all[,3]), "%Y%m%d"), "%Y")
# taking only annual report based classification
class_all <- class_all[class_all$mr_info_full_name=="Annual Report",]
# inserting column of nic two digit code
nic_code_two_digit <- as.numeric(substr(as.character(class_all[,5]), 1, 2))
class_all <- cbind(class_all,nic_code_two_digit)
# preparing for merging the data class_all and sales_all
colnames(class_all)[1] <- "prowess_code"
colnames(sales_all)[1] <- "prowess_code"
colnames(class_all)[3] <- "year"
colnames(sales_all)[3] <- "year"
colnames(sales_all)[2] <- "company_name"
# merging class_all and sales_all
sales_by_class_all <- merge(x = sales_all, y = class_all, by = c("prowess_code","year","company_name"),all.x = TRUE)
# keeping only the relevant columns in the data
sales_by_class_all <- sales_by_class_all[,c(1,2,3,6,10)]
# appending a column of "<>" for market_share to sales_by_class
market_share <- rep("<>",nrow(sales_by_class))
sales_by_class <- cbind(sales_by_class,market_share)
# calculating market share for each cell and writing it to the data
for (i in 1:nrow(sales_by_class)){
  if ((is.na(sales_by_class[i,4]) == TRUE)|is.na(sales_by_class[i,5]) == TRUE){
    sales_by_class[i,6] <- NA
  }
  else
    sales_by_class[i,6] <- {sales_by_class[i,4]/sum(subset(sales_by_class_all, (year == sales_by_class[i,2]) & (nic_code_two_digit == sales_by_class[i,5]), sa_sale_of_goods),na.rm = TRUE)}*100
}
# write.csv(sales_by_class,"./market_share.csv")
# year 2023 has smaller base and missing observation so dropping it for comparable visualization
sales_by_class <- sales_by_class[sales_by_class$year!="2023",]
# also dropping 2016 as it is not to be analysed
sales_by_class <- sales_by_class[sales_by_class$year!="2016",]
# reading market share as a number
sales_by_class[,6] <- as.numeric(sales_by_class[,6])
# reading prowess_code as text
sales_by_class[,1] <- as.character(sales_by_class[,1])
# classifying the companies based on average turnover for the period under consideration.
# the average turnover considered is the pre-COVID period that is 2017-19.
# creating a data set with average turnover
library(tidyverse)
sales_avg <- sales[sales$year == "2017"|sales$year == "2018"|sales$year == "2019",]
sales_avg <- sales_avg %>% group_by(prowess_code) %>% summarise(avg_turnover = mean(sa_sale_of_goods,na.rm = TRUE))
# adding firm_size based on MSME Act 
for(i in 1:73){
  if (sales_avg$avg_turnover[i] <= 50){
    sales_avg$firm_size[i] <- "Micro"
  }
  else{
    if(sales_avg$avg_turnover[i] <= 500){
      sales_avg$firm_size[i] <- "Small"
    }
    else{
      if(sales_avg$avg_turnover[i] <= 2500){
        sales_avg$firm_size[i] <- "Medium"
      }
        else{
          sales_avg$firm_size[i] <- "Large"
      }
    }
  }
}
# merging data set of firm_size so that the heat maps can be drawn by firm size category
sales_by_class <- merge(x = sales_by_class, y = sales_avg, by = "prowess_code", all.x = TRUE)
# plotting heat map for all firms
# for this the data needs to be transformed
market_share <- reshape(sales_by_class, idvar = c("company_name","prowess_code"), timevar = "year", drop = c("sa_sale_of_goods","nic_code_two_digit","avg_turnover","firm_size"),direction = "wide")
colnames(market_share) <- c("prowess_code","company_name","2017","2018","2019","2020","2021","2022")
rownames(market_share) <- market_share[,1] 
x <- as.matrix(market_share[,-c(1,2)])
heatmap(x, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code")
# plotting a heat map for firms classified as large
market_share_large <- reshape(subset(sales_by_class, firm_size == "Large"), idvar = c("company_name","prowess_code"), timevar = "year", drop = c("sa_sale_of_goods","nic_code_two_digit","avg_turnover","firm_size"),direction = "wide")
colnames(market_share_large) <- c("prowess_code","company_name","2017","2018","2019","2020","2021","2022")
rownames(market_share_large) <- market_share_large[,1] 
y <- as.matrix(market_share_large[,-c(1,2)])
heatmap(y, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code")
# plotting heat map for firms classified as medium
market_share_medium <- reshape(subset(sales_by_class, firm_size == "Medium"), idvar = c("company_name","prowess_code"), timevar = "year", drop = c("sa_sale_of_goods","nic_code_two_digit","avg_turnover","firm_size"),direction = "wide")
colnames(market_share_medium) <- c("prowess_code","company_name","2017","2018","2019","2020","2021","2022")
rownames(market_share_medium) <- market_share_medium[,1] 
z <- as.matrix(market_share_medium[,-c(1,2)])
heatmap(z, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code")
# plotting heat map for firms classified as small
market_share_small <- reshape(subset(sales_by_class, firm_size == "Small"), idvar = c("company_name","prowess_code"), timevar = "year", drop = c("sa_sale_of_goods","nic_code_two_digit","avg_turnover","firm_size"),direction = "wide")
colnames(market_share_small) <- c("prowess_code","company_name","2017","2018","2019","2020","2021","2022")
rownames(market_share_small) <- market_share_small[,1] 
w <- as.matrix(market_share_small[,-c(1,2)])
heatmap(w, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code")
# to plot heat map by the category of the beneficiary the data is transformed as follows
scheme <- read.csv("./PLISFPI.csv")
scheme <- scheme[is.na(scheme$Prowess.Code) == FALSE,]
colnames(scheme)[11] <- "prowess_code"
colnames(identity)[1] <- "prowess_code"
identity <- merge(x = identity, y = scheme, by = "prowess_code", all.x = TRUE)
# removing some less useful columns
identity <- identity[,-c(7,8,22,23,24)]
identity <- identity[,-19]
# merging category details with sales data
sales_by_class <- merge(x = identity, y = sales_by_class, by = c("prowess_code","company_name"), all.x = TRUE)
# heat map for category 1 
market_share_cat1 <- reshape(subset(sales_by_class,Category == "Category 1"),idvar = c("company_name","prowess_code"), timevar = "year", drop = c("co_industry_gp_code","co_industry_name","nic_prod_code","nic_name","Category","RTE..RTC","F..V","Marine","Mozzerrella.Cheese","Innovative","Organic","B.M","CIN","NIC.Code","Year.of.Incorporation","CMIE.Footprint","sa_sale_of_goods","nic_code_two_digit","avg_turnover","firm_size"),direction = "wide")
colnames(market_share_cat1) <- c("prowess_code","company_name","2021","2019","2020","2017","2018","2022")
rownames(market_share_cat1) <- market_share_cat1[,1]
market_share_cat1 <- market_share_cat1[,c("prowess_code","company_name","2017","2018","2019","2020","2021","2022")]
v <- as.matrix(market_share_cat1[,-c(1,2)])
heatmap(v, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code")
# heat map for category 3
market_share_cat3 <- reshape(subset(sales_by_class,Category == "Category 3"),idvar = c("company_name","prowess_code"), timevar = "year", drop = c("co_industry_gp_code","co_industry_name","nic_prod_code","nic_name","Category","RTE..RTC","F..V","Marine","Mozzerrella.Cheese","Innovative","Organic","B.M","CIN","NIC.Code","Year.of.Incorporation","CMIE.Footprint","sa_sale_of_goods","nic_code_two_digit","avg_turnover","firm_size"),direction = "wide")
colnames(market_share_cat3) <- c("prowess_code","company_name","2021","2019","2020","2017","2018","2022")
rownames(market_share_cat3) <- market_share_cat3[,1]
market_share_cat3 <- market_share_cat1[,c("prowess_code","company_name","2017","2018","2019","2020","2021","2022")]
u <- as.matrix(market_share_cat3[,-c(1,2)])
heatmap(u, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code")
```

```{r all, echo=FALSE}
heatmap(x, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code",main = "All firms")
```
```{r large,echo=FALSE}
heatmap(y, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code",main = "Large firms")
```
```{r medium,echo=FALSE}
heatmap(z, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code", main = "Medium firms")
```
```{r small,echo=FALSE}
heatmap(w, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code", main = "Small firms")
```
```{r cat1,echo=FALSE}
heatmap(v, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code", main = "Category 1")
```
```{r cat3,echo=FALSE}
heatmap(u, Colv = NA, Rowv = NA, scale="row",xlab = "Year", ylab = "Prowess Code", main = "Category 3")
```

## References

